---
title: "Consensus Network Results Analysis"
author: ""
date: ""
output: 
  html_document:
    fig_height: 3
    fig_width: 5
---
```{r include=FALSE}
library(DataComputing)
```

To use this script, make sure your CSV file follows the format of the file located in `/Users/jann/github/BrainProject_2016/Consensus Networks/staticnetworkresults.csv`. 

Variable inputs
```{r}
filename = "/Users/jann/github/BrainProject_2016/ConsensusNetworks/staticnetworkresults.csv"
```


Reads the CSV file into a table. Keeps only the entries whose first column follows the pattern [1 or 2 numerical values][A or B][1 or 2 numerical values]. In essence, this gets rid of the non-consensus network entries.
```{r}
table = read.csv(filename, header=TRUE)
table = table[grepl("[0-9]{1,2}[AB][0-9]{1,2}", table[,1]),]
table
head(table)
df = table %>% extractMatches("([0-9]{1,2})[AB][0-9]", X) %>% extractMatches("[0-9]{1,2}([AB])[0-9]", X) %>% extractMatches("[0-9]{1,2}[AB]([0-9]{1,2})", X)
colnames(df) <- c("OG", "AUC", "ACC", "sum", "AUCweight", "MeanOrMedian", "TopK")

head(df)
findbestOperation = df %>% group_by(MeanOrMedian) %>% summarise(mean(AUC))
findbestOperation
```

```{r}
meanOnly = df %>% filter(MeanOrMedian=="A")
meanOnly
```

```{r}
findbestWeight = meanOnly %>% group_by(AUCweight) %>% summarise(mean(AUC))
findbestWeight
findbestTop = meanOnly %>% group_by(TopK) %>% summarise(mean(AUC))
findbestTop
```

```{r}
library(gridExtra)
jpeg("WeightedSumResults.jpg")
grid.table(findbestWeight)
dev.off()

```

