---
title: "Lnear CombinationS of AUC and ACC"
author: "Tiffany Jann"
date: ''
output:
  html_document:
    fig_height: 3
    fig_width: 5
  pdf_document: default
---
```{r include=FALSE, echo=FALSE}
library(DataComputing)
library(stringr)
library(xtable)
```

*BEGIN INPUT*

Paste the AUC Ranks results from calling `TopMethods(path)` in MATLAB. (In MATLAB: you would want to set `path` to the folder containing all your results. Remember that the output of `TopMethods` takes the average, so if you wanted to see the result of just one data set, put that result folder in an empty shell folder, and call `TopMethods` on the shell folder's path. You can get the path by calling `path = pwd`.)
```{r echo=FALSE}
aucranks = "
BCorrD     [8601]
Genie      [8510]
BCohF      [8170]
Tigress    [7980]
BCorrU     [7968]
PCohF      [7688]
BH2D       [7432]
BTED       [7087]
BH2U       [7025]
BTEU       [6769]
PTED       [6690]
PTEU       [5988]
BMITD2     [5606]
PMITD2     [5585]
PMITD1     [5514]
PH2U       [5497]
PH2D       [5418]
PCorrD     [5240]
BMITD1     [4761]
PMITU      [4571]
AS         [4034]
BMITU      [3973]
MVAR       [3952]
pCOH2      [3853]
Smvar      [3702]
hmvar      [3628]
dDTF       [3619]
PDC        [3361]
Af         [3206]
oPDCF      [3193]
COH1       [3190]
COH2       [3157]
GC         [2663]
PCorrU     [2529]
DC1        [2528]
CondGC     [2497]
DTF        [2423]
ffDTF      [2423]
GGC        [2344]
PGC        [2317]
GPDC       [2310]
BCohW      [ 400]
PCohW      [ 400]
pCOH1      [ 400]
"
```

Paste the ACC Ranks results from calling `TopMethods(path)` in MATLAB.
```{r echo=F}
accranks = "
BCorrD     [8209]
Genie      [7916]
Tigress    [7727]
BTEU       [6258]
BTED       [6254]
PMITD2     [6244]
BMITD2     [6238]
PMITD1     [6231]
PTED       [6211]
PTEU       [6106]
BMITD1     [6055]
PCorrD     [5843]
MVAR       [5732]
hmvar      [5729]
dDTF       [5722]
PDC        [5699]
BH2D       [5698]
Af         [5688]
oPDCF      [5676]
DC1        [5653]
GGC        [5651]
CondGC     [5636]
GC         [5621]
AS         [5616]
GPDC       [5614]
PGC        [5601]
DTF        [5582]
ffDTF      [5582]
PH2D       [5574]
BCohF      [2631]
BCorrU     [2612]
PCohF      [2500]
BH2U       [2364]
PH2U       [1795]
Smvar      [1723]
BMITU      [1713]
PMITU      [1705]
pCOH2      [1641]
COH2       [1604]
COH1       [1564]
PCorrU     [1541]
BCohW      [ 400]
PCohW      [ 400]
pCOH1      [ 400]
"
```
*END INPUT*



Extracting the AUC and ACC values from the strings aucranks and accranks above, and maintaining the order.
```{r}
AUC = as.numeric(unlist(str_extract_all(aucranks, "[0-9]{2,9}")))
AUC
ACC = as.numeric(unlist(str_extract_all(accranks, "[0-9]{2,9}")))
ACC
```

Extracting the AUC and ACC method names from the respective strings and maintaining order. This is necessary because the order for AUC and ACC differ.
```{r}
aucname = gsub("[0-9]{2,3}", "", aucranks)
aucname = str_extract_all(aucname, "[:alnum:]{2,}")
aucname
accname = gsub("[0-9]{2,3}", "", accranks)
accname = str_extract_all(accname, "[:alnum:]{2,}")
accname
```

Creating the AUC and ACC data frames.
```{r}
aucDF = data.frame(aucname, AUC)
colnames(aucDF) <- c("Method", "AUC")
head(aucDF)

accDF = data.frame(accname, ACC)
colnames(accDF) <- c("Method", "ACC")
head(accDF)
```

Combining the two data frames so each method has its corresponding AUC and ACC values in one table.
```{r}
df = inner_join(aucDF, accDF, by=c("Method"="Method"))
```

Creating columns for each weighted sum.
```{r}
df$"(0.1,0.9)" <-  1/10 *df$AUC + (1 - 1/10) *df$ACC
df$"(0.2,0.8)" <-  2/10 *df$AUC + (1 - 2/10) *df$ACC
df$"(0.3,0.7)" <-  3/10 *df$AUC + (1 - 3/10) *df$ACC
df$"(0.4,0.6)" <-  4/10 *df$AUC + (1 - 4/10) *df$ACC
df$"(0.5,0.5)" <-  5/10 *df$AUC + (1 - 5/10) *df$ACC
df$"(0.6,0.4)" <-  6/10 *df$AUC + (1 - 6/10) *df$ACC
df$"(0.7,0.3)" <-  7/10 *df$AUC + (1 - 7/10) *df$ACC
df$"(0.8,0.2)" <-  8/10 *df$AUC + (1 - 8/10) *df$ACC
df$"(0.9,0.1)" <-  9/10 *df$AUC + (1 - 9/10) *df$ACC

df
```

Write results to file. Outputs a LaTeX code that will construct table and a csv table. `WeightedSumsAUCACC.tex` and `WeightedSumsAUCACC.csv`.
```{r}
print(xtable(df, caption=c("Different weighted sums of (AUC,ACC) metrics."), digits=1), type="latex", include.rownames=FALSE, file="WeightedSumsAUCACC.tex")

write.csv(df, file = "WeightedSumsAUCACC.csv", row.names = F)
```

